Apparent preferences for cognitive effort fade when multiple forms of effort and delay are interleaved in a foraging environment

### 2020-08-05 Cost_manuscript.Rmd
rewriting sequential history

  All analyses were performed in R 3.5.2 (CITE). First we tested whether decision makers integrated delay and reward information. To address the prediction that participants would be more likely to accept higher reward and shorter handling time trials, we fit a logistic regression to each participant’s data to predict trial-wise acceptances, using handling time and reward amount as predictors. The resulting beta coefficients for handling time and reward were pooled across all participants, and we performed a one-sample rank-sum test on each set of coefficients to examine whether they were significantly positive or negative (compared to no effect of 0). We then performed an extension of the logistic regression by adding an autoregressive covariate containing the number of consecutive quits prior to a given trial. This examined the possibility that participant choices were governed by recent quitting history rather than the experimental parameters. Coefficients significantly different from 0 denoted that a participant relied on recent quitting history.

@@

  To address the first hypothesis, we examined whether increasing handling times and reward amounts produced the expected reduction and increase in acceptance probabilities, respectively. Since participants in the effort groups were forced to travel when they failed to perform above threshold (see Methods), we distinguish between acceptances (entering the handling period) and completions (successfully obtaining a reward). Individual-specific logistic regression coefficients for handling time were significantly lower than 0 (mean $\beta$ = `r round(mean(coeffRH_mean[2], na.rm = T), digits = 2)`, SE = `r round(coeffRH_se[2], digits = 2)`; Wilcoxon test: V = `r rankHand$statistic`, *p* `r report_p(rankHand$p.value)`), whereas increasing the reward amount predicted higher acceptance probabilities (mean $\beta$ = `r round(coeffRH_mean[1], digits = 2)`, SE = `r round(coeffRH_se[1], digits = 2)`; Wilcoxon test: V = `r rankOffer$statistic`, p `r report_p(rankOffer$p.value)`). We next examined whether choices could also have been affected by recent choice history (i.e. if too many sequential quits promoted acceptances regardless of reward amount) by adding a regressor to the model that tracked the number of consecutive quits preceding a trial. This auto-regressive coefficient was not significantly different than 0 (mean $\beta$ = `r round(coeffRHAR_mean[3], digits = 2)`, SE = `r round(coeffRHAR_se[3], digits = 2)`; Wilcoxon test: V = `r rankRHAR$statistic`, p `r report_p(rankRHAR$p.value)`), and the 95% confidence interval (CI) of these coefficients contained 0 in `r round((sum(AR_CIs) / nSubjs_btw) * 100)`% of our participants. This indicates that offer patterns did not systematically influence participant behavior.

>>>>

  All analyses were performed in R 3.5.2 (CITE). First we tested whether decision makers integrated delay and reward information. **To address the prediction that participants would be more likely to accept higher reward and shorter handling time trials, we fit a logistic regression to each participant’s data to predict trial-wise acceptances, using handling time and reward amount as predictors. The resulting beta coefficients for handling time and reward were pooled across all participants, and we performed a one-sample rank-sum test on each set of coefficients to examine whether they were significantly positive or negative (compared to no effect of 0). We then performed an extension of the logistic regression by adding an autoregressive covariate containing the number of consecutive quits prior to a given trial. This examined the possibility that participant choices were governed by recent quitting history rather than the experimental parameters. Coefficients significantly different from 0 denoted that a participant relied on recent quitting history.**

@@

  **new** We performed a mixed effects logistic regression to address the first hypothesis. Since participants in the effort groups were forced to travel when they failed to perform above threshold (see Methods), we distinguish between acceptances (entering the handling period) and completions (successfully obtaining a reward). Larger reward amounts significantly increased acceptance probabilities ($\beta$ = ), whereas longer delays decreased them (), in line with predictions. Two additional regressors showed that 1) having missed out on several consecutive rewards decreased the probability of acceptance (how?) and 2) participants became more selective when recent history was richer (). Model selection using Akaike's Information Criterion (AIC) suggested that participants were influenced by the 5 most recent rewards.

  **old** We performed a mixed effects logistic regression to address the first hypothesis. Since participants in the effort groups were forced to travel when they failed to perform above threshold (see Methods), we distinguish between acceptances (entering the handling period) and completions (successfully obtaining a reward). Individual-specific logistic regression coefficients for handling time were significantly lower than 0 (mean $\beta$ = `r round(mean(coeffRH_mean[2], na.rm = T), digits = 2)`, SE = `r round(coeffRH_se[2], digits = 2)`; Wilcoxon test: V = `r rankHand$statistic`, *p* `r report_p(rankHand$p.value)`), whereas increasing the reward amount predicted higher acceptance probabilities (mean $\beta$ = `r round(coeffRH_mean[1], digits = 2)`, SE = `r round(coeffRH_se[1], digits = 2)`; Wilcoxon test: V = `r rankOffer$statistic`, p `r report_p(rankOffer$p.value)`). We next examined whether choices could also have been affected by recent choice history (i.e. if too many sequential quits promoted acceptances regardless of reward amount) by adding a regressor to the model that tracked the number of consecutive quits preceding a trial. This auto-regressive coefficient was not significantly different than 0 (mean $\beta$ = `r round(coeffRHAR_mean[3], digits = 2)`, SE = `r round(coeffRHAR_se[3], digits = 2)`; Wilcoxon test: V = `r rankRHAR$statistic`, p `r report_p(rankRHAR$p.value)`), and the 95% confidence interval (CI) of these coefficients contained 0 in `r round((sum(AR_CIs) / nSubjs_btw) * 100)`% of our participants. This indicates that offer patterns did not systematically influence participant behavior.
